Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-16 talk/iwtc11/paper.tex
loop peeling does more than loop-invariant code motion, add an XXX
use official name of this optimization

@@

\subsection{Pure operation reuse}
If a pure operation appears more than once in the trace with same input
arguments, it only needs be executed the first time and then the result
can be reused for all other appearances. When that is combined with loop
peeling, the single execution of the operation is placed in the
preamble. That is, loop invariant pure operations are moved out of the
loop. The interactions here are the same as in the previous
section. That is, a vector, $H$, of variables produced in the preamble
and used in the peeled loop needs to be constructed. Then the jump and
input arguments are updated according to
Equation~\ref{eq:heap-inputargs} and Equation~\ref{eq:heap-jumpargs}.

>>>>

XXX loop peeling does a lot more than loop-invariant code motion
% take this loop as an example:
% [i1, i2]
% i3 = i1 + 1
% i4 = i2 + 1
% escape(i4)
% jump(i2, i3)
% none of the operations is loop-invariant, but loop peeling will still remove the second addition

@@

\subsection{Common Subexpression Elimination}
If a pure operation appears more than once in the trace with same input
arguments, it only needs be executed the first time and then the result
can be reused for all other appearances. When that is combined with loop
peeling, the single execution of the operation is placed in the
preamble. That is, loop invariant pure operations are moved out of the
loop. The interactions here are the same as in the previous
section. That is, a vector, $H$, of variables produced in the preamble
and used in the peeled loop needs to be constructed. Then the jump and
input arguments are updated according to
Equation~\ref{eq:heap-inputargs} and Equation~\ref{eq:heap-jumpargs}.
